pema application

### 2022-12-05 paper/manuscript.Rmd
adapted horseshoe section

A regularizing prior distribution shrinks small coefficients towards zero by assigning high probability mass to near-zero values.
There are many different regularizing prior distributions,
some of which are analogous to specific frequentist methods [@vanErpOberskiMulder2019].
For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
Both the frequentist LASSO penalty and the Bayesian LASSO prior have a tuning parameter $\lambda$ that controls the amount of regularization.
In frequentist LASSO, its value is usually chosen via cross-validation [@hastieElementsStatisticalLearning2009]. 
In the Bayesian approach, by contrast,
its value can be optimized during model estimation.

<span id = "horseshoe">One limitation of the LASSO prior is that it biases all regression coefficients towards zero - for relevant as well as irrelevant moderators.
To overcome this limitation, regularizing priors with better shrinkage properties have been developed.
These priors still pull small regression coefficients towards zero,
but exert less bias on larger regression coefficients.
One example is the horseshoe prior [@CarvalhoPolsonScott2010].
It has heavier tails than the LASSO prior,
which means that it does not shrink (and therefore bias) substantial coefficients as much.
One limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
The regularized horseshoe was introduced to overcome this limitation [@PiironenVehtari2017b].</span></span>

>>>>

A regularizing prior distribution shrinks small coefficients towards zero by assigning high probability mass to near-zero values.
There are many different regularizing prior distributions,
some of which are analogous to specific frequentist methods [@vanErpOberskiMulder2019].
For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
Both the frequentist LASSO penalty and the Bayesian LASSO prior have a tuning parameter $\lambda$ that controls the amount of regularization.
In frequentist LASSO, its value is usually chosen via cross-validation [@hastieElementsStatisticalLearning2009]. 
In the Bayesian approach, by contrast,
its value can be estimated during model estimation.

<span id = "horseshoe">One limitation of the LASSO prior is that it biases all regression coefficients towards zero - for relevant as well as irrelevant moderators.
To overcome this limitation, regularizing priors with better shrinkage properties have been developed.
These priors still pull small regression coefficients towards zero,
but exert less bias on larger regression coefficients.
One example is the horseshoe prior [@CarvalhoPolsonScott2010].
It has heavier tails than the LASSO prior,
which means that it does not shrink (and therefore bias) substantial coefficients as much.
Two limitations of the horseshoe prior are 1) it lacks a formal way to include prior information regarding the degree of sparsity; and 2) it does not regularize coefficients far from zero. While the second problem is often considered a strength of the horseshoe prior, it can result in convergence issues when parameters are weakly identified.
The regularized horseshoe was introduced to overcome these limitations [@PiironenVehtari2017b].</span></span>
